Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-15 exp1/present2013.tex
simplify experiment description
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@683 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{frame}{Constraints on scope of experiment}

Above all: Easy to understand for newcomers to DoE!

\begin{itemize}
\item Just 2 levels.
\item Handful of illustrative factors.
\item Analysis that illustrates key concepts.
\item Straightforward to program and reproduce.
\item Artificial performance differences.
\end{itemize}

\begin{frame}{Choices to meet these constraints}

  \begin{itemize}
  \item Response variable: Time from DNS lookup finishes to endpoint
    has delivered a full response, measured by \texttt{curl}.
  \item We don't compare different implementions, we compare the
    performance before and after some change.
  \item Query engine: \texttt{4store} where we insert \textsf{sleep}
    statements in the join function on one level and language matching
    function on the other. 
  \end{itemize}

@@

\item Average over all the 32 level-combinations of the environmental
  factors.

\item May create a one-sided two-sample t-test with 4 values for each
  of the levels of ``Implement''.
\item Lends support to $H_1$ with a high probability, $p=1.16 \cdot
10^{-7}$.

>>>>

\begin{frame}{The experiments}

\textbf{Main goal}: Easy to understand for newcomers to DoE!

\begin{block}{Description}
  Experiment with 8 factors, 2 levels where we compare a single SPARQL
  implementation before and after some change. We used \texttt{4store}
  where we insert \textsf{sleep} statements in the join function on
  one level and language matching function on the other, to simulate
  an optimization that may have detrimental side-effects.

\end{block}

@@

\item May create a one-sided two-sample t-test with 4 values for each
  of the levels of ``Implement'' based on averages of other factors.
\item Lends support to $H_1$ with a high probability, $p=1.16 \cdot
10^{-7}$.
